\section{Analysis of the Impacts of Fungal Diversity}
In the previous analysis and prediction, we obtained the predicted value of decomposition rate under different combinations of fungi. Compared with decomposition rates of the five fungi living alone, it is found that the decomposition rates of the fungal combinations is significantly higher than that of the single species of fungi living alone.
\par
In the combination $F_A\ \&\ F_B$, although both are drought-tolerant fungal species suitable for arid or semi-arid climates, they still maintain a certain degree of decomposition ability in the arboreal or tropical rain forests environments, the predicted decomposition rate of which after $200$ days is $24.4\%$. In the combination $F_D\ \&\ F_E$, although both are water-requiring fungal species suitable for arboreal and tropical rain forests climates, they can still maintain the capacity to decompose lignin or cellulose in the arid and semi-arid regions, the predicted decomposition rate of which after $200$ days is $22.1\%$.
\par
It could be inffered from the analysis above that when the diversity of fungal population~\cite{population} is further improved, the total decomposition rate in the area where the fungi are located would increase significantly. The diversity of fungal communities could greatly improve the overall efficiency of a certain system with respect to the breakdown of ground litter.
\par
Since drought-tolerant fungi can survive in hot flashes, and water-requiring fungi can also live in arid areas, it is possible to introduce fungal species in a certain area as much as possible as long as ensuring that there is no harm such as biological invasion. By doing so to respond to varying degrees of changes in the local natural environment.
\par
For instance, if the five fungi distribute in the tropical rain forests, as the destruction of the rainforest by humans intensifies, the environment of the rainforest deteriorates with moisture decreasing and temperature rising. At this time, drought-tolerant species $F_A$ and $F_B$ would play their superior role to maintain the stability of the decomposition process in the rainforest ecosystem as much as possible, and avoid that the carbon cycle~\cite{carboncircle} is out of balence.