\begin{thebibliography}{99}
  \addcontentsline{toc}{section}{References}
  \bibitem{researchonfungi}Nicky Lustenhouwer, Daniel S. Maynard, Mark A. Bradford, Daniel L. Lindner, Brad Oberle, Amy E. Zanne, and Thomas W. Crowther, “A trait-based understanding of wood decomposition by fungi,” Proceedings of the National Academy of Sciences of the United States, May 13, 2020. https://www.pnas.org/content/pnas/117/21/11551.full.pdf
  \bibitem{chemicalreactions}Kabuyah, Rachel. The Decomposition of Organic Matter in Soils by Fungi[D]. United Kingdom:The University of Manchester,2013.
  \bibitem{lignin}Henderson, Moira Elizabeth Keill. Physiological studies of fungi concerned in the decomposition of lignin and related compounds[D]. United Kingdom:University of Aberdeen,1955.
  \bibitem{cellulose}Christiane Liers, Caroline Bobeth, Marek Pecyna, etc. DyP-like peroxidases of the jelly fungus Auricularia auricula-judae oxidize nonphenolic lignin model compounds and high-redox potential dyes[J]. Applied Microbiology and Biotechnology,2010.
  \bibitem{initialsize}Wikipedia. Fungus[EB/OL].https://simple.wikipedia.org/wiki/Fungus,2020-12-30.
  \bibitem{physics}David J. Griffiths. Introduction to Electrodynamics[M]. Prentice Hall:United States of America,1999:39-50.
  \bibitem{literature}D. Hawksworth. Global species numbers of fungi: are tropical studies and molecular approaches contributing to a more robust estimate[J]. Biodiversity and Conservation,2012.
  \bibitem{R2}Hiriote, Sasiprapa. Multivariate concordance correlation coefficient[D]. United States of America:The Pennsylvania State University,2009.
  \bibitem{logisticmodel}Nath, Gopal Chandra. Logistic regression model and case study[D]. United States of America:Lamar University - Beaumont,2014.
  \bibitem{multigroups}Shang, Justin. Model Assessments in Logistic Regression[D]. United States of America:University of Wyoming,2019.
  \bibitem{land}Ghuneim, Lydia-Ann John. Distribution, Diversity, and Function of Filterable Microorganisms in the Conwy River[D]. United Kingdom:Bangor University,2020.
  \bibitem{gray}Wu, Zhao Yang. Stock Index Prediction Based on Grey Theory, Arima Model and Wavelet Methods[D]. Canada:Concordia University,2010.
  \bibitem{population}Wikipedia. Biodiversity[EB/OL].https://simple.wikipedia.org/wiki/Biodiversity,2021-1-16.
  \bibitem{carboncircle}Wikipedia. Carbon cycle[EB/OL].https://simple.wikipedia.org/wiki/Carbon\_cycle,2021-1-16.
\end{thebibliography}